### 2020-05-29 serial.tex
take break!

\fref{rR} shows Euler-Lotka estimates of \Ro\ on different definitions of the serial interval. 
When the initial forward serial-interval distributions $f_0(\tau)$ is used, estimates (from \eref{Rforward}) exactly match the (correct) generation-interval-based estimates (\eref{Rgen} for all values of the correlation $\rho$ between the intrinsic incubation period and the intrinsic generation interval (\fref{rR}A).
When the intrinsic distributions are used, however, estimates based on the serial interval (\eref{Rintrinsic});
as $r$ increases, \Rintrinsic saturates and eventually decreases due to negative serial intervals (\fref{rR}B).
While the forward serial intervals during the exponential growth phase can also be negative, the proportion of negative intervals are appropriately balanced because faster epidemic growth will lead to shorter backward incubation periods (and therefore a lower proportion of negative serial intervals).

>>>>

\fref{rR} shows Euler-Lotka estimates of \Ro\ on different definitions of the serial interval. 
When the initial forward serial-interval distributions $f_0(\tau)$ is used, estimates (from \eref{Rforward}) exactly match the (correct) generation-interval-based estimates (\eref{Rgen} for all values of the correlation $\rho$ between the intrinsic incubation period and the intrinsic generation interval (\fref{rR}A).
When the intrinsic distributions are used, however, estimates based on the serial interval (\eref{Rintrinsic}) underestimate \Ro; as $r$ increases, \Rintrinsic saturates and eventually \emph{decreases} due to the increasing inferred importance of negative serial intervals (\fref{rR}B).
While the forward serial intervals during the exponential growth phase can also be negative, their effects are appropriately balanced because faster epidemic growth leads to longer serial intervals (and a corresponding lower proportion of negative intervals).
